---
title: "My First post"
author: "Jayleen Sanchez"
date: "2025-08-08"
categories: [education,stress]
---

Hello everyone!

This is my project on my introduction to R. I will be focusing on the factors that cause students stress in relation to their academic performance.

1.  Introduction

I am going to be diving into student stress and how it affects their performance. I will be focusing on teacher-student relationships and if it affects the students performance, as well as, if academic pressure or social support have a bigger impact on the students stress.

These questions matter because understanding the cause of the student’s stress is important to help improve educational outcomes, health, and retention. In particular, academic success can be shaped not only by student effort but also by the relationship they have with instructors. Teacher-student relationships are often overlooked but it could be the main cause of both stress and performance.

I predict that the students who don’t have a close relationship with their teachers will have a lower academic performance compared to those who have a closer relationship and that social support has a bigger impact on the student’s stress than academic pressure.

2.  Methods

This data set was collected from a nationwide survey that consisted of 843 college students ranging from ages 18-21 answering questions about their experiences with stress, health, relationships, academics, and emotional well-being. The data was collected via a google form using a five-point Likert scale ("Not at all" to "Extremely") and anonymized to protect privacy

2.  Results

```{r}
library(tidyverse)
mydata <- read.csv("StressLevelDataset.csv")

# Graph comparing academic performance to Student/Teacher relationships

Relationship_vs_Academic <- ggplot(mydata, mapping = aes(x = teacher_student_relationship, y = academic_performance, color = stress_level)) + geom_jitter(width = 0.2, alpha = 0.4) + geom_smooth(method = "lm", se = FALSE, color = "blue") + labs(title = "Teacher/Student Relationship vs Academic Performance", x = "Teacher/Student Relationship", y = "Academic Performance")

Relationship_vs_Academic
ggsave("Relationship_vs_Academic.png")


```

```{r}

# academic pressure vs student stress
ggplot(mydata, mapping = aes(x = study_load, y = stress_level, color = social_support)) + geom_point(position = "jitter") + geom_smooth(method = "lm") + labs(title = "Relationship Between Study Load, Social Support, and Stress Level" )

#ggplot(mydata, aes(x = study_load)) +
#  geom_histogram(binwidth = 1)
```
